The development of infants' responses to mispronunciations - A Meta-Analysis

### 2019-01-11 Paper_Analyses.Rmd
added power/sample size for interaction

The estimated effect for mispronunciation sensitivity in this meta-analysis is `r mp_effect`, and the most frequently observed sample size is `r median_sample` participants. If we were to assume that researchers assess mispronunciation sensitivity in a simple ANOVA, the resulting power is `r r2(pat$power)`. Reversely, to achieve 80% power, one would need to test `r round(pat.est$n, 1)` participants. These calculations suggest that for the comparison of responses for correct pronunciations and mispronunciations, the studies included in this meta-analysis contain well-powered analyses. However, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which will require even larger sample sizes. We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity.

>>>>

The estimated effect for mispronunciation sensitivity in this meta-analysis is `r mp_effect`, and the most frequently observed sample size is `r median_sample` participants. If we were to assume that researchers assess mispronunciation sensitivity in a simple ANOVA, the resulting power is `r r2(pat$power)`. Reversely, to achieve 80% power, one would need to test `r round(pat.est$n, 1)` participants. These calculations suggest that for the comparison of responses for correct pronunciations and mispronunciations, the studies included in this meta-analysis contain well-powered analyses. However, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates requre four times the sample size to detect an effect of similar magnitue as the main effect for both ANOVA [@Fleiss1986] and mixed-effect-model [@Leon2009] analyses. We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity.

### 2019-01-11 Paper_Analyses.tex
added power/sample size for interaction

The estimated effect for mispronunciation sensitivity in this
meta-analysis is 0.50, and the most frequently observed sample size is
24 participants. If we were to assume that researchers assess
mispronunciation sensitivity in a simple ANOVA, the resulting power is
0.92. Reversely, to achieve 80\% power, one would need to test 17
participants. These calculations suggest that for the comparison of
responses for correct pronunciations and mispronunciations, the studies
included in this meta-analysis contain well-powered analyses. However,
many studies in this meta-analysis included further factors to be
tested, leading to two-way interactions (age versus mispronunciation
sensitivity is a common example), which will require even larger sample
sizes. We thus strongly advocate for a consideration of power and the
reported effect sizes to test infants' mispronunciation sensitivity.

@@

@@

>>>>

The estimated effect for mispronunciation sensitivity in this
meta-analysis is 0.50, and the most frequently observed sample size is
24 participants. If we were to assume that researchers assess
mispronunciation sensitivity in a simple ANOVA, the resulting power is
0.92. Reversely, to achieve 80\% power, one would need to test 17
participants. These calculations suggest that for the comparison of
responses for correct pronunciations and mispronunciations, the studies
included in this meta-analysis contain well-powered analyses. However,
many studies in this meta-analysis included further factors to be
tested, leading to two-way interactions (age versus mispronunciation
sensitivity is a common example), which by some estimates requre four
times the sample size to detect an effect of similar magnitue as the
main effect for both ANOVA (Fleiss, 1986) and mixed-effect-model (Leon
\& Heo, 2009) analyses. We thus strongly advocate for a consideration of
power and the reported effect sizes to test infants' mispronunciation
sensitivity.

@@

\hypertarget{ref-Fleiss1986}{}
Fleiss, J. L. (1986). \emph{The Design and Analysis of Clinical
Experiments}. New York: Wiley; Sons.

@@

\hypertarget{ref-Leon2009}{}
Leon, A. C., \& Heo, M. (2009). Sample sizes required to detect
interactions between two binary fixed-effects in a mixed-effects linear
regression model. \emph{Computational Statistics and Data Analysis},
\emph{53}(3), 603--608.
doi:\href{https://doi.org/10.1016/j.csda.2008.06.010}{10.1016/j.csda.2008.06.010}
